### 2016-03-30 manuscript.Rnw
reformat abstract according to guidelines

While phylogenies have been getting easier to build, it has been difficult to
re-use, combine, and synthesize the information they provide because published
trees are often only available as image files, and taxonomic information is not
standardized across studies. The Open Tree of Life (OTL) project addresses these
issues by providing a digital tree that encompasses all organisms, built by
combining taxonomic information and published phylogenies. The project also
provides tools and services to query and download parts of this synthetic tree,
as well as the source data used to build it. Here, we present \texttt{rotl}, an
R package to search and download data from the Open Tree of Life directly in
R. \texttt{rotl} uses common data structures allowing researchers to take
advantage of the rich set of tools and methods that are available in R to
manipulate, analyze, and visualize phylogenies.

>>>>

\begin{enumerate}
\item While phylogenies have been getting easier to build, it has been difficult
  to re-use, combine, and synthesize the information they provide because
  published trees are often only available as image files, and taxonomic
  information is not standardized across studies.
\item The Open Tree of Life (OTL) project addresses these issues by providing a
  digital tree that encompasses all organisms, built by combining taxonomic
  information and published phylogenies. The project also provides tools and
  services to query and download parts of this synthetic tree, as well as the
  source data used to build it. Here, we present \texttt{rotl}, an R package to
  search and download data from the Open Tree of Life directly in R.
\item \texttt{rotl} uses common data structures allowing researchers to take
  advantage of the rich set of tools and methods that are available in R to
  manipulate, analyze, and visualize phylogenies. Here, and in the vignettes
  accompanying the package, we demonstrate how \texttt{rotl} can be used with
  other R packages to analyze biodiversity data.
\item As phylogenies are being used in a growing number of applications,
  \texttt{rotl} facilitates access to phylogenetic data, and allows their
  integration with statistical methods and data sources available in R.
\end{enumerate}
